---
title: "Analysis 2"
output: html_notebook
---

Here I will focus on the model that involves the custom MICS only.
This notebook uses the inputs generated on the analysis notebook.

## What is the best combination of T, H and C ?

Let's try out a bunch of scenarios.
As benchmarker, I will use the average absolute error and the RMSE and plot it over each week of data that we have.

```{r}
rmse = function(m, o){
  sqrt(mean((m - o)^2))
}

benchmarkAll <- function(model) {
  errs <- data.frame(timestamp = round1$timestamp, reference = round1$refNO2, fitted = predict(model, round1))
  errs <- rbind(errs, data.frame(timestamp = round2$timestamp, reference = round2$refNO2, fitted = predict(model, round2)))
  errs <- rbind(errs, data.frame(timestamp = round3$timestamp, reference = round3$refNO2, fitted = predict(model, round3)))
  
  errs <- errs[which(abs(errs$fitted) < 100), ]
  
  errs$week <- floor(difftime(errs$timestamp, errs[1, 'timestamp'], units=c('week')))
  
  weeks <- c()
  meanerrs <- c()
  rmses <- c()
  
  for(week_ in unique(errs$week)) {
    weeks <- append(weeks, week_)
    meanerr_ <- mean(abs(errs[errs$week == week_, 'reference'] - errs[errs$week == week_, 'fitted']))
    meanerrs <- append(meanerrs, meanerr_)
    rmse_ <- rmse(errs[errs$week == week_, 'reference'], errs[errs$week == week_, 'fitted'])
    rmses <- append(rmses, rmse_)
  }
  
  print(paste('Average error', mean(meanerrs)))
  print(paste('Average rmse', mean(rmses)))
  
  plot(weeks, meanerrs, type="l", col="red3", ylab='err', ylim=c(min(meanerrs, rmses), max(meanerrs, rmses)))
  points(weeks, rmses, col="black")
  legend("topleft",
       legend=c('mean err', "rmse"),
       lty=c(1,0), pch=c(NA, 16), col=c("red3", "black"))
}
```


Model 1: custom_MICS * temperature + custom_MICS * humidity

```{r}
model <- lm(refNO2 ~
              custom_MICS * temperature +
              custom_MICS * humidity
            , data=round1)
summary(model)

benchmarkAll(model)
```


Model 2: custom_MICS_sq + custom_MICS * temperature + custom_MICS * temperature_sq + custom_MICS * humidity + custom_MICS * humidity_sq

```{r}
model <- lm(refNO2 ~
              custom_MICS_sq + 
              custom_MICS * temperature +
              custom_MICS * temperature_sq +
              custom_MICS * humidity +
              custom_MICS * humidity_sq
            , data=round1)
summary(model)

benchmarkAll(model)
```

Model 3: custom_MICS + temperature + humidity

```{r}
model <- lm(refNO2 ~
              custom_MICS + temperature + humidity
            , data=round1)
summary(model)

benchmarkAll(model)
```

Model 4: custom_MICS + custom_MICSxT + custom_MICSxH

```{r}
model <- lm(refNO2 ~
              custom_MICS + custom_MICSxT + custom_MICSxH
            , data=round1)
summary(model)

benchmarkAll(model)
```
This last one is quite interesting.
Temperature and humdity, in principle, shouldn't have direct effect over NO2.
But this is a little bit worse than the results with temperature and humidity as a direct input.


Model 5: custom_MICS + custom_MICS_sq + custom_MICSxT + custom_MICSxH

```{r}
model <- lm(refNO2 ~
              custom_MICS + custom_MICS_sq + custom_MICSxT + custom_MICSxH
            , data=round1)
summary(model)

benchmarkAll(model)
```

This is actually the best for now.

Model 6: custom_MICS_sq + custom_MICS * temperature + custom_MICS * humidity

```{r}
model <- lm(refNO2 ~
              custom_MICS_sq + custom_MICS * temperature + custom_MICS * humidity
            , data=round1)
summary(model)

benchmarkAll(model)
```

Not better.


Let's see if things get better if we consider powers of the multiplications:

```{r}
round1$custom_MICSxT_sq <- round1$custom_MICSxT ^ 2
round1$custom_MICSxH_sq <- round1$custom_MICSxH ^ 2
round2$custom_MICSxT_sq <- round2$custom_MICSxT ^ 2
round2$custom_MICSxH_sq <- round2$custom_MICSxH ^ 2
round3$custom_MICSxT_sq <- round3$custom_MICSxT ^ 2
round3$custom_MICSxH_sq <- round3$custom_MICSxH ^ 2
```


Model 7: custom_MICS + custom_MICS_sq + custom_MICSxT + custom_MICSxT_sq + custom_MICSxH + custom_MICSxH_sq

```{r}
model <- lm(refNO2 ~
              custom_MICS + custom_MICS_sq +
              custom_MICSxT + custom_MICSxT_sq +
              custom_MICSxH + custom_MICSxH_sq
            , data=round1)
summary(model)

benchmarkAll(model)
```

It doesn't get any better.


Model 8: custom_MICS + custom_MICS_sq + custom_MICS_cu + custom_MICSxT + custom_MICSxH

```{r}
model <- lm(refNO2 ~
              custom_MICS + custom_MICS_sq + custom_MICS_cu +
              custom_MICSxT +
              custom_MICSxH
            , data=round1)
summary(model)

benchmarkAll(model)
```

The cubic power of custom_MICS doesn't do anything.


## And the winner is...

I think the winner is:

custom_MICS + custom_MICS_sq + custom_MICSxT + custom_MICSxH

It also makes sense.
It means that NO2 depends on custom MICS, its second power and its multiplication by temperature and humidity.
Maybe there are some complex interactions between mics, temperature and humidity, but those are hard to capture with a simple instrument like this.


## What is the best sampling frequency?

This is a bit trickier because we will have to resample all the signals and compute the benchmarks again.

We'll fix the model to the winner chosen before.

```{r}

'30 mins'




```



